Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/related_work.tex
fixed { error

\subsection{Smartphones}
Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones. Research shows that perceptions of risk change as computing systems change. Chin et. al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, finding that these attitudes differ significantly ~\cite{chin2012measuring}. How people use these smartphones was also unlike other computing systems. Palen et. al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use cite\{palen2000going}. People also perceive and behave without a realistic understanding of the risks they are taking. Felt et. al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.

>>>>

\subsection{Smartphones}
Many researchers have attempted to study user concerns about security or privacy issues associated with their smartphones. Research shows that perceptions of risk change as computing systems change. Chin et. al\ investigate how user attitudes toward security and privacy for smarphones differ from attitudes for traditional computing systems, finding that these attitudes differ significantly ~\cite{chin2012measuring}. How people use these smartphones was also unlike other computing systems. Palen et. al\ track smartphone users for six weeks to find rapid modifications in behaviors with respect to context and the social appropriateness of phone use \cite{palen2000going}. People also perceive and behave without a realistic understanding of the risks they are taking. Felt et. al\ examine the Android permission system and find that 17\% of participants paid attention to permissions, and only 3\% comprehended what these permissions meant.
